---
title: "Probability question"
author: "Aftab A Sorwar"
format: html
editor: visual
---

## question:

Is the probability of winning on the first roll higher than the probability of winning in two or more throws?


### solution
Here the input will be:
     N - Number of games to simulate in each run of run_craps_simulation
     R - Number of repetitions to calculate probabilities
and the output will be:
       - Probability of winning on the first roll
       - Probability of winning in two or more rolls
       

```{r}
simulate_probabilities <- function(N, R) {
  
  first_roll_wins <- 0
  multi_roll_wins <- 0
  total_wins <- 0
  
  for (i in 1:R) {
    results <- run_craps_simulation(N)
    
    first_roll_wins <- first_roll_wins + sum(results$n_roll == 1 & results$outcome == "win")
    multi_roll_wins <- multi_roll_wins + sum(results$n_roll > 1 & results$outcome == "win")
    total_wins <- total_wins + sum(results$outcome == "win")
  }
  
  prob_first_roll_win <- first_roll_wins / total_wins
  prob_multi_roll_win <- multi_roll_wins / total_wins
  
  return(cbind(
    prob_first_roll_win = prob_first_roll_win,
    prob_multi_roll_win = prob_multi_roll_win
  ))
}
```

```{r}
simulate_probabilities(N = 10, R = 100)
```


